\documentclass[../main/Replicate.tex]{subfiles}
\begin{document}
\section{Discussion}
	\subsection{Comparison between the three web forms}
	\subsubsection{Control condition - Index1}
	The purpose of this study was to improve usability of web form filling of insurance claims and find which of three web forms layouts was the most usable. When analysing the results it can be noted that index1 was the least mentally demanding web form, according to the mental demand scale of NASA-TLX(Table \ref{nasa-tlx}), and objective measure of mean Hbo activation(Fig. \ref{fig:mean-hbo-index123}), and the SAM arousal scale(statistical significance $p=0.049$ compared to index3). However, the calculated total tlx indicated higher perceived workload than index2, and lower than index3. Index1 can be said to support the consistency heuristic\cite{nielsen1990heuristic} because it was the control condition and represented a standard insurance claim form. The comparatively low workload measured for index1 can be attributed to the fact that the task was familiar, and therefore participants had to spending less working memory resources on planning because the task sequence was already mapped in their brain. One participant supported this argument by saying: \textit{``I consider it more logical, like logical approach..to say who you are, what happened to your car and then what happened exactly, describe it from your own perspective.''}. Also, 4 users reported that the sequence of small question first, leading to the description at the end, helped them to recall the situation better: \textit{``I preferred the first(index1) and third(index3) examples, as they asked more general questions at the beginning. This made me think about what aspects to include in the event summary at the end, such as number of cars involved''}. Which means that the sequence of web forms or their order of presentation is important aspect to consider when designing long web forms.
	
	Index1 induced the least perceived emotional valence from the SAM questionnaire, compared to the rest of the conditions, with marginal significance of $p=0.073$ when compared to index3. However, the objective data from the fNIRS differences demonstrated higher left hemisphere activation than index2, and slightly less than index3. Similarly, it took more time to complete the web form compared to index2, and slightly less time than index3.	
	
	\subsubsection{Description at beginning - Index2}
	Generally, index2 elicited the least workload inferred from the mean Hbo concentration, total tlx, perceived effort, physical demand, and frustration measures(Table \ref{nasa-tlx}). Also, users performance was higher in index2, as the task completion time was the lowest, although not statistically significant(see Fig. \ref{fig:mean-task-completion-time}). One interpretation is that index2 supported participants working memory better, specifically for this study design, because index2 presents the description field first, thus lowering the time to hold the visual information in the episodic memory. Consequently, users memory was relatively fresher when filling the description field in index2, which demanded the most attentional capacity, compared to the rest of the conditions. 
	
	Furthermore, index2 elicited approximately neutral emotional valence rating(3.40) which was higher than index1(3.10) and lower than index3(3.70), see Figure \ref{fig:sam-valence-index123}. In contrast, the objective data from fNIRS differences reveal more right hemisphere activation which can be interpreted as more negatively valenced affect or avoidance motivation. The last finding can be supported with the fact that only 3 out of 20 participants expressed preference for index2. A possible explanation is that index2 did not support the consistency heuristic\cite{nielsen1990heuristic,shneiderman1992designing} because the description field is normally situated at the end of insurance claim forms. This statement can be supported by the following participant comments: \textit{``The only one I didn't like is the first one(index2) particularly. It was just describing the event before filling out the details it is a bit awkward.''}, and another participant stated:\textit{``Index1 and Index3 were Ok, but I didn't like index2 because I was not used to it.''}.
	
	\subsubsection{Divided form - Index3}
	We found out that index3 to elicits the highest mental workload according to the fNIRS Hbo data, SAM arousal scale(significant difference with index1), total tlx, mental demand scale from NASA-TLX. Also, it takes the most time to complete the task compared to the rest of the conditions. However, index3 was evoking the highest positive valence(SAM), fNIRS differences were indicating more left hemisphere activation, and users preferred it the most when asked after the finish of the experiment. The results were contradictory according to the Norman\cite{norman2002emotion} positive affect should enhance operator creativity, thus increasing the performance.
	
	Also, it can be noted that perceived temporal demand for index3 was lower than index1 and index2(no statistical significance). This can be attributed to the fact that index3 had lower number of forms(visual cues) on each page. It can be inferred that the more web forms are present on an interface, the more the user perceives temporal demand because it appraises the situation as one that needs more work to be performed. This claim can be supported with the feedback from the participants: \textit{``so the second one(index3) I felt having to click the links broke it down a little bit, like you didn't have to think about everything in one go...''} or other user expressed \textit{``you give all the details and then you take your time to write about the incident so you don't feel very rushed or something''}. 
	
	\subsubsection{Divided vs single page approach}
	A division can be made between the web forms which contain all forms on one page(index1, index2), and web forms which are consolidated or divided on several pages(index3). We define these as the \textit{single page approach}, and the \textit{divided page approach}.
	
	A possible explanation of the higher positive emotional valence estimated across all measures for the divided page approach is that users had to process less informational cues at a time, which they appraised as positive experience. As one of the participants mentioned \textit{``because you don't have to think about the other forms''}. So having less web forms displayed on one screen improves visual search, decreases clutter, which imposes less temporal demand on the task, according to our data. Consequently, users might 
	appraise the task as more positively valenced because it spends less attentional resources for meta-cognition.
	
	One advantage of the single page approach is that participants can go back and verify what information they have already entered: \textit{``I remember in the second one(index1) I'm not sure whether the option provided left or right, so I rechecked''}. This way working memory resources are saved because participants has the ability to quickly recheck what they have already entered, relying on recognition, rather than recall\cite{nielsen1990heuristic}. Another advantage of the single page approach is that participants can choose which form to start first: \textit{``the good thing about the number two(index1) is everything is on the same page I can choose whatever I like''}. Generally, some of the participants preferred to fill in the description field first, and then the rest of the forms, so researchers and practitioners have to give users the power to choose from where they can start. However, in our case the participants watched a recorded accident that they had to recall after approximately 2 minutes. In reality, the delay between the accident and the claim form filling will be much higher, thus the arrangement of the web forms depends on the time between the accident and the claim form filling.
	
	In our opinion, index1 is suitable for implementation because it elicited less mental workload in 3 out of 4 measures for workload, and the 10 out of 20 users expressed that their prefer it. Also, index1 met the consistency heuristic, it gave more control and freedom to the users by letting them choose from which form to start first. 	
	Furthermore, index3 should also be considered appropriate for real life implementation because it produced most positive valence according to our subjective(SAM) and objective(mean Hbo differences) measures. In addition, 11 out of 20 users favoured this web form. We could not conclude which of the two approaches provides better user experience because single paged approach was less mentally demanding, and slightly less preferred, in contrast to index3 which required the most attentional resources, but it received the most positive results(\textit{``When I was filling the forms I think the second one(index3) is the easiest.''}). Furthermore, as it is not clear how mental workload or emotional valence affects the user experience we cannot conclude which is web form is more important. Also the question of what should evaluators try to minimize: the perceived workload or the negative valenced responses, remains unanswered.
	
	\subsection{fNIRS practicality for HCI evaluations}
	One of the aims of the study was to assess the feasibility of fNIRS for HCI evaluation studies. After analysing the fNIRS data from 20 participants we had to exclude 9 because of bad data. However, we were close to reaching statistical significance between the three conditions as the p value was $p=0.054$ with only 11 subjects examined. This gives promising results that fNIRS can be used as reliable objective measure for workload in usability studies. We propose that a study needs approximately 20 participants, in order to reach statistical significance, however that is four times more than the suggested 5 users tests by Virzi\cite{virzi1992refining}. It should be noted that this recommendation highly depends on study design, and some studies may require only 10 subjects, while others more than 30.
	
	Other advantage of fNIRS is that it provides continuous measure of the Hbo concentration in the PFC, thus it can be highly suitable for detecting distinct periods of overload. For example, it can be particularly useful in game studies where participants should stay in the flow\cite{nakamura2002concept} state. Also, functionally the flow experience has been suggested to be situated in the prefrontal cortex and medial temporal lobe\cite{dietrich2004neurocognitive}, consequently fNIRS can be used to measure it. Accordingly, researchers should be able to detect moments where the challenge of the game is either too difficult or too easy.
	
	When considering the measurement of emotional valence by comparing the hemodynamic activation between the left and right hemispheres was can conclude that we were unsuccessful as we were far from statistical significance($p=0.681$). More focused research should be conducted in order to test this approach.
	
	In conclusion, fNIRS provides useful data, however we can infer about design issues from user trials, and receive rich data for relatively less amount of money compared to the more expensive and time consuming fNIRS evaluation study. From the brain scanner we receive single continuous measure which can be interpreted in various ways, but still gives only limited data about the hemodynamic activity, which itself is not well understood in cognitive neuroscience. Consequently, fNIRS has limited practicality for evaluating neutral web interfaces, like web forms because it requires more time and financial resources, and gives relatively vague data, compared to the established methods, like user trials which are cheap to conduct, less time consuming and provide rich data. However, as noted above fNIRS appears to be particularly useful in game evaluation studies where the continuous measure will provide valuable information about the level of engagement\cite{harrivel2013monitoring} and the flow states\cite{yoshida2014brain} of players.
	\subsection{Implications for Design}
	Based on the obtained results we propose the following recommendations for design of long web forms:
	\begin{itemize}
		\item Include visual representations of information where possible, rather than display it as text only:\\
		Some participants did not knew the names of the different body parts of a car and a few even used search engine to see what the different words like, bonnet and bumper meant. To address this problem, we propose that a visualisation of car divided on its main body parts should be depicted on the form in order to support recognition.
		
		\item Sequence of web forms is important aspect to consider, so testing the order of presentation of forms may yield important information:\\
		Some of the participants wanted to fill different form fields first, and scrolled down to find them. Consequently, researchers should consider which questions to ask first, and which last in their web forms.
		
		\item Divide a long web forms onto separate pages if the information entered in each field is not relative to the other fields, or when the users do not need to check what they have entered previously:\\
		During the web form filling process it can be noted that participants occasionally inspect what they have written before, in order to verify that information or check what they had written before. Designers should take into account as the behaviour described above was often observed.
	\end{itemize}
	
	\subsection{Limitations of the study}
	This study attempts to simulate real conditions, by simulating automotive accident and then presenting a insurance claim form to fill. Participants wait approximately 2 minutes after they watch a video to start filling the web form. In real situations the delay between the accident and the form filling is usually higher. Therefore, it lacks ecological validity. Watching videos of automotive accidents may also have biased the subjective ratings of participants when they had to rate the web forms.
	
	One of the disadvantages of near infrared scanning technology is that, in order to collect reliable measurements the emitter-detector pairs have to be in contact with the skin constantly, 
	
	It should be noted that we had difficulties with the fNIRS device, as some of the channels did not worked reliably. Therefore, we had to exclude a large amount of participant data that was defective or incomplete. As a result, we obtained less statistical power from the results. However, this was a problem encountered because of malfunctioning of the particular device, and not problem encompassing all fNIRS based systems. In addition, the fNIRS device which we used was slightly invasive and wearing it caused pain and discomfort, after approximately 30-40 minutes. As a result, we had to design our experimental protocol so that the duration does not exceed 40 minutes.
	
	\subsection{Future work}
	To produce more valid results, experiments without the inclusion of videos should be conducted. For example testing the insurance quote process, instead of claims. Also, the divided page approach should be further examined because it produced encouraging and positive results, except that it required the most attentional resources. However, as it is not clear which improves the user experience more, the workload experienced or the positive or negative appraisal of the interface, we should further test and diagnose the single versus divided page approaches.
	\subsection{Conclusion}
	In summary, we used functional near infrared spectroscopy in a user study of the web form filling process of insurance claim. We aimed to obtain objective and subjective measurements of mental workload and emotional valence. We tested the web page layout by producing 3 variations. After conducting the experiment the standard single page web form which was the control condition, showed the least mental workload, according ot the majority of objective and subjective measures that we used to infer it. On the other hand, the web form which was divided on three separate pages, yielded highest workload compared to the rest of conditions but elicited most positively valenced ratings, and was most preferred by participants. However, we could not determine which of the web forms is more suitable for implementation, as we are uncertain which is more important for long forms: to elicit positive affect, or to be less mentally demanding. However, the answer is varies for the different interfaces and implementations. Consequently, experiments should be conducted to examine the difference between single and divided page approaches for long web forms in more details. Also, we assessed the practicality of fNIRS for similar web interface studies to be limited. In addition, we could not reliably measure the level of emotional valence with fNIRS in this particular experiment. Finally, we outlined implications for design for long web forms, discussed the disadvantage of the study and the future work that should be done.
\end{document}